\section{Motivation}
\label{sec:motivation}

% that increasing computation power in mobile 
% Recent studies \cite{url4} still report that the median page load time for a mobile website 
% is about 14 seconds. Research \cite{url4} shows that a user will only wait for 3 seconds 
% before abandoning a web site if it shows no response at all. A lot of prior work \cite {njait2016www}
% has been done to compare the page load times on mobile vs desktop, and recent results
% from 2016 claim that despite the increasing compute resources in mobile devices,
% the computation time on mobile is significantly higher than their desktop counterparts. 
Computation power in mobile devices has dramatically improved over
the course of past years. However, recent work~\cite{njait2016www}
claims that PLT on mobile devices is not proportional to the
increasing computation capability of those devices, compared to PLT on
resource-rich desktops.  The consequence of such disproportion is
well-addressed in recent report~\cite{url4}. The authors report that median
PLT for mobile websites is 14 seconds and claim that end-users
tolerate PLT latency for 3 seconds on the average untill ``leaving'' a
website, which negatively influences companies' revenue~\cite{revenue}.
Thus, high PLT on mobile devices degrades user-experience and comes at
monetary loss. Given that more than half of web traffic is generated
from mobile devices~\cite{traffic}, reducing PLT is critical.

% Chrome released a paper last year showing how improved caching algorithms, despite having 
% significant improvements on the desktop, don't have the same proportionate improvements 
% on mobile devices. This is primarily attributed to the fact that computation comprises more than 65\%
% of the critical path during a page load. This illustrates the need to further optimize the computation 
% time. 
Computation time is dominant factor in improving PLT.  Recent
work~\cite{chrome} highlights that enhanced caching algorithms
significantly improve performance in desktop environment, where
computation-power is plentiful. In comparison, PLT of mobile devices
is improved by relatively small fraction. The authors describe that
because computation consists at least 65\% of PLT,
resource-constrained mobile devices benefit less from the caching
algorithms. 
% Recent effort from industry has been focused on 
% Major web browsers like Chrome, Firefox, and Safari have recenlty invested a lot of resources,
% time and energy into improving web performance on mobile devices, specifically by targeting 
% the network usage. However, the network now comprises less than 30\% \cite{njait2016www} of the total critical
% path for an average page load on a mobile device. 
% This includes caching almost 95\% of the
% resources that are fetched from the server \cite{vesuna2016caching}, dns presolution, dns caching, tcp reconnect etc.

Further, recent effort from industry to improve mobile web performance
has been focused on reducing network usage, under assumption that
network is dominant factor in PLT. However, recent
study~\cite{njait2016www} shows that the network latency composes of
less than 30\% of the total PLT. The authors note that not only the
performance of mobile network improved but also numerous
optimizations (e.g., resource caching~\cite{vesuna2016caching}, DNS
presolution and caching, TCP Fast reconnection) contribute to reduce
the network latency.

Aforementioned prior works suggest that for mobile devices,
computation time is the most dominant factor in total PLT.  These key
findings motivate our work to investigate the main bottleneck in
current computation time in mobile devices and to build a system that
caches computation for Javascript.

\section{Study in computation time}
% During the Chrome dev summit this year, their team announced the latest improvements they have 
% made in their browser to improve the page load time. Interestingly, most of their work focuses on
% improving the compilation and parsing time by introducing compile and parser cache. 
 % Our experiments
% on the most popular news and sports websites on the latest mobile hardware and the latest 
% Chrome version reveal that despite these recent efforts, scripting still takes significantly more
% time ,as compared to the other components of the total computation time. With our understanding of 
% computation being the current bottleneck for high page load times, 
% we conduct a set of experiments to evaluate the reasons for this
% exceedingly high computation time. In order to do this, we break down computation
% into four categories: scripting, loading, painting, and rendering.
% and observe that scripting essentially takes more than 70\% of the total
% computation time which is more than all the other categories combined (Figure 3). 
% This makes it all the more important to do an in-depth analysis of the computation time to clearly
% understand where exactly this time is being spent. Using results from this study, we would eventually
% design our caching framework for the javascript execution output. 


We conducted a study of computation time for browsing popular news and
sports websites. \todo{add methodology}

The result suggests the bottleneck in high PLT comes from computation
time. Also, we conducted micro-benchmark to break
down PLT into four main categories: scripting, loading, painting, and
rendering. The micro-benchmark provides useful insight about elements
of computation time. First, script time consists of 70\% of total PLT,
\todo{is this correct reference to the figure?}
as shown in Fig.~\ref{fig:properties-sec}. Our study suggests that
most of PLT on mobile devices stems from scripting time. Note that our
study does not include network time, which can be another potential
source of PLT.

